%! Author = alex
%! Date = 11/26/22

% Preamble
\documentclass[../Aleksandr Kuznetsov CV.tex]

% Packages
%\usepackage{amsmath}

% Document
\begin{document}

    \subsection{PyRL\hfill}\label{subsec:project-pyrl}\\
    \location{2021 – Present}
    \href{https://github.com/AlKuz/PyRL}{https://github.com/AlKuz/PyRL}\\
    Pet-project to learn Reinforcement Learning and make RL more convenient to use.
    \sectionsep

    \subsection{Chat-Bot for medical data access\hfill}\label{subsec:project-buddy}\\
    \location{Mar 2022 – Present}
    Chatbot for simplifying access to the large medical document storage.
    The chatbot is working on top of existing searching tool.
    Implemented data collection backend and labelling pipeline.
    \sectionsep

    \subsection{Medical data collection and reporting\hfill}\label{subsec:project-cancer}\\
    \location{Oct 2021 – Mar 2022}
    Loading diseases data from side aggregator to collect all updates and help medical staff be aware of last clinical
    researches.
    I was responsible for project architecture development, leaded DS team, provided code reviews and implemented core
    components.
    \sectionsep

    \subsection{Intelligent financial analysis systems\hfill}\label{subsec:project-ifa}\\
    \location{2020 – 2021}
    My own pet project to analyze stock assets.
    Using Yahoo Finance API to get information about assets.
    Connect to the broker via API, get portfolio data and rebalance assets.
    Developed microservices architecture for the project.
    \sectionsep

    \subsection{Classification and processing of emails\hfill}\label{subsec:project-emails}\\
    \location{Mar 2021 – Oct 2021}
    Classification and processing of email messages to help support team and generating reports for managers.
    During the project I developed data processing architecture and research pipeline, leaded DS team, provided code
    reviews and implemented half of the pipeline components.
    \sectionsep

    \subsection{Object detection on the video of urban\\infrastructure survey\hfill}\label{subsec:project-sewerage}\\
    \location{Apr 2020 – Feb 2021}
    Developed data labelling pipelines, trained and deployed different Computer Vision models (classification,
    segmentation and object detection tasks).
    Implemented simple UI based on Streamlit to discuss labelling process and quality with the customer.
    \sectionsep

    \subsection{Seismological observation data analysis\hfill}\label{subsec:project-seismo}\\
    \location{Mar 2020 – Mar 2020}
    Create models to improve the quality of seismology images.
    \sectionsep

    \subsection{Fraud detection in financial transactions\hfill}\label{subsec:project-fraud}\\
    \location{Feb 2020 – Feb 2020}
    Developed data preprocessing, validation and feature generation pipeline.
    \sectionsep

    \subsection{Computer vision system for car parking\hfill}\label{subsec:project-parking}\\
    \location{Sep 2018 – Dec 2019}
    Detecting and tracking objects from IP camera video.
    I was developing a backend for video processing, writing logic of interactions between objects, and sending events
    to the main business processes server.
    \sectionsep

    \subsection{Research and Development of Control Systems \\for Micro Gas Turbine Engines\hfill}\label{subsec:project-mgtd}\\
    \location{Sep 2015 – Feb 2017}
    Thermodynamic modeling of micro gas turbine engines, research and development of control systems for this ones
    \sectionsep

    \subsection{Diploma project "Development of a Mathematical \\Model LPRE Units and Research Engine Dynamic\\
    Characteristics"}\label{subsec:project-diploma}\\
    \location{Sep 2014 – Feb 2015}
    Modeling of Rocket Engine and its control system using Matlab Simulink.
    \sectionsep

\end{document}